### 2024-06-01 2024-5-13/sections/implementation.tex
change heuristics to optimizations in the experiment chapter

\subsection{Empirical justification of the technical choices and heuristics}\label{subsec:size_reduction_eval}
We also do experiments to evaluate the effectiveness of the automata size-reduction techniques for register-representable regexes, that is, Step 2 of Section~\ref{subsec:cefadec}. We practically answer why we choose LIA formula to solve the nonemptiness problem instead of using the nuXmv model checker like \cite{atva2020}. Finally, we carry out experiment on the ComplexCounting benchmarks to justify the heuristics of Section~\ref{sec:heuristic} for non-register-representable regexes.
\subsubsection{Empirical justification of the technical choices}
%We also do experiments to evaluate the effectiveness of the automata size-reduction techniques, that is, Step 2 in Section~\ref{subsec:cefadec}. 
%Let us use $\ostrichrecl_{\rm -SIMP}$ to denote $\ostrichrecl$ with the size-reduction techniques removed. 
We compare $\ostrichrecl$ with its variant  ${\rm +NUXMV}$. ${\rm +NUXMV}$  is obtained from $\ostrichrecl$ by using the nuXmv model checker to solve the nonemptiness of $\cefadec$.

The experiment results can be found in Table~\ref{tab:results_heuristic}. We can see that $\ostrichrecl$ solves 2,532 more instances and is 2.38 times faster than ${\rm +NUXMV}$. Therefore, the decision procedure in Section~\ref{subsec:cefadec} is more efficient to solve the $\cefadec$ problem than nuXmv. 
\begin{table}
  \import{tables}{table_heuristics.tex}
  \caption{Empirical justification of the technical choices and heuristics}\label{tab:results_heuristic}
\end{table}

@@

\subsubsection{Empirical justification of the heuristics for non-regesiter-representable regexes} 
We also compare the performance of $\ostrichrecl$ with its variants ${\rm -NEST}$, ${\rm -COMP}$, ${\rm -FIND}$. ${\rm -NEST}$ is obtained from $\ostrichrecl$ by removing the heuristic for nested counting. ${\rm -COMP}$ is obtained by removing the heuristic for complement on counting operators. ${\rm -FIND}$ is obtained by removing the heuristic for finding the accepted word of the automaton.

@@

From the results, the heuristic for complement on counting operators and the heuristic for finding the accepted word of the automaton are more effective than the heuristic for nested counting. Futhermore, the heuristic for complement on counting operators contributes both to satisfiable and unsatisfiable instances, while the heuristic for finding the accepted word and the heuristic for nested counting contribute only to satisfiable instances.
All the heuristics improve the performance of $\ostrichrecl$.

\begin{table}
  \import{tables}{table_heuristics_complex.tex}
  \caption{Empirical justification of the heuristics on ComplexCounting benchmarks}\label{tab:results_heuristic_complex}
\end{table}

>>>>

\subsection{Empirical justification of the technical choices and optimizations}\label{subsec:size_reduction_eval}
We also do experiments to evaluate the effectiveness of the automata size-reduction techniques for register-representable regexes, that is, Step 2 of Section~\ref{subsec:cefadec}. We practically answer why we choose LIA formula to solve the nonemptiness problem instead of using the nuXmv model checker like \cite{atva2020}. Finally, we carry out experiment on the ComplexCounting benchmarks to justify the optimizations of Section~\ref{sec:heuristic} for non-register-representable regexes.
\subsubsection{Empirical justification of the technical choices}
%We also do experiments to evaluate the effectiveness of the automata size-reduction techniques, that is, Step 2 in Section~\ref{subsec:cefadec}. 
%Let us use $\ostrichrecl_{\rm -SIMP}$ to denote $\ostrichrecl$ with the size-reduction techniques removed. 
We compare $\ostrichrecl$ with its variant  ${\rm +NUXMV}$. ${\rm +NUXMV}$  is obtained from $\ostrichrecl$ by using the nuXmv model checker to solve the nonemptiness of $\cefadec$.

The experiment results can be found in Table~\ref{tab:results_heuristic}. We can see that $\ostrichrecl$ solves 2,532 more instances and is 2.38 times faster than ${\rm +NUXMV}$. Therefore, the decision procedure in Section~\ref{subsec:cefadec} is more efficient to solve the $\cefadec$ problem than nuXmv. 
\begin{table}
  \import{tables}{table_heuristics.tex}
  \caption{Empirical justification of the technical choices and optimizations}\label{tab:results_heuristic}
\end{table}

@@

\subsubsection{Empirical justification of the optimizations for non-regesiter-representable regexes} 
We also compare the performance of $\ostrichrecl$ with its variants ${\rm -NEST}$, ${\rm -COMP}$, ${\rm -FIND}$. ${\rm -NEST}$ is obtained from $\ostrichrecl$ by removing the heuristic for nested counting. ${\rm -COMP}$ is obtained by removing the heuristic for complement on counting operators. ${\rm -FIND}$ is obtained by removing the heuristic for finding the accepted word of the automaton.

@@

From the results, the heuristic for complement on counting operators and the heuristic for finding the accepted word of the automaton are more effective than the heuristic for nested counting. Futhermore, the heuristic for complement on counting operators contributes both to satisfiable and unsatisfiable instances, while the heuristic for finding the accepted word and the heuristic for nested counting contribute only to satisfiable instances.
All the optimizations improve the performance of $\ostrichrecl$.

\begin{table}
  \import{tables}{table_heuristics_complex.tex}
  \caption{Empirical justification of the optimizations on ComplexCounting benchmarks}\label{tab:results_heuristic_complex}
\end{table}
